
```{r}
install.packages("tidyverse")
```
```{r}
library(tidyverse)
```
```{r}
students<-read_csv("student_performance.csv")
```
```{r}
View(students)
```
```{r}
head(students)
```
```{r}
dim(students)
```
```{r}
str(students)
```
```{r}
summary(students)
```
```{r}
colSums(is.na(students))
```
```{r}
table(students$Gender)
table(students$Result)
table(students$PartTimeJob)
```
```{r}
mean(students$FinalExamScore)
median(students$FinalExamScore)
```
```{r}
cor(students$StudyHoursPerWeek, students$FinalExamScore)
cor(students$AttendancePercent, students$FinalExamScore)
cor(students$SleepHoursPerNight, students$FinalExamScore)
```
```{r}
ggplot(students, aes(x = FinalExamScore)) +
geom_histogram(binwidth = 5, fill = "steelblue",color = "white") +
labs(title = "Distribution of Final Exam Scores",
x = "Final Exam Score", y =" Number of Students")
```
```{r}
ggplot(students, aes(x = Result, fill = Result)) +
geom_bar() +
labs(title = "Number of Students: Pass vs Fail",
x = "Result", y = "Number of Students")
```
```{r}
ggplot(students, aes(x = PartTimeJob, y = FinalExamScore, fill = PartTimeJob)) +
geom_boxplot() +
labs(title = "Final Exam Score by Part-Time Job Status",
x = "Has a Part-Time Job?", y = "Final Exam Score")
```
```{r}
ggplot(students, aes(x = StudyHoursPerWeek, y = FinalExamScore)) +
geom_point(color ="darkorange", alpha = 0.7) +
geom_smooth(method = "lm", se = FALSE, color = "black") +
labs(title =";Study Hours vs Final Exam Score",
x = "Study Hours per Week", y ="Final Exam Score")
```
```{r}
ggsave("study_hours_vs_score.png", width = 7, height = 5, dpi = 300)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
